Javelins with hyper3 objects

### 2025-12-29 inst/javelin.Rmd
start talking about max in BT

Above, we see that Chopra threw 87.03m on his first throw, 87.58m on
his second, and so on.  Vadlejch threw 83.98m on his first throw, etc.
We may convert this to a named vector with elements being the throw
distances, and names being the competitors:

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on.  `NA` entries correspond to no-throws.  It
is easy to plot the data in visual form:

@@

>>>>

Above, we see that Chopra threw 87.03 on his first throw, 87.58 on his
second, and so on (all measurements are in meters).  Vadlejch threw
83.98 on his first throw, etc.  We may convert this to a named vector
with elements being the throw distances, and names being the
competitors:

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58 and 87.03 respectively;
Vadlejch threw the third-longest throw of 86.67, and so on.  `NA`
entries correspond to no-throws.  It is easy to plot the data in
visual form:

@@

# Discussion: maximum throw vs Bradley-Terry philosophy

The competition is won by the player who has the longest throw: the
sufficient statistic would be the maximum of the six attempts.
Bradley-Terry cannot handle this if different players have different
variance: short throws are disregarded.

As an example, suppose two throwers have normally distributed
distances; thrower A has a smaller mean distance than thrower B but a
larger variance.  Numerically:

```{r}
set.seed(0)
thrower_A <- round(rnorm(6, 80.2, 2.6), 2)
thrower_B <- round(rnorm(6, 80.3, 1.3), 2)
D <- as.attemptstable(as.data.frame(rbind(thrower_A, thrower_B)))
D
apply(D, 1, max)
```

Above we see that thrower A wins, despite having a smaller mean
distance.
